### 2016-04-02 document/manuscript-plos.tex
add Kai to author list

Yasset Perez-Riverol\textsuperscript{1,*}
Laurent Gatto\textsuperscript{2},
Rui Wang\textsuperscript{1}, 
Timo Sachsenberg \textsuperscript{3},
Julian Uszkoreit\textsuperscript{4},
Felipe da Veiga Leprevost\textsuperscript{5},
Christian Fufezan\textsuperscript{6},
Tobias Ternent\textsuperscript{1},
Stephen J. Eglen\textsuperscript{7}, 
Daniel S. Katz\textsuperscript{8}, 
Tom J. Pollard\textsuperscript{9}, 
Alexander Konovalov\textsuperscript{10},
Robert M Flight\textsuperscript{11},
Juan Antonio Vizcaíno\textsuperscript{1,*}

@@

\bf{1} European Molecular Biology Laboratory, European Bioinformatics
Institute (EMBL-EBI), Wellcome Trust Genome Campus, Hinxton,
Cambridge, CB10 1SD, UK.
\\
\bf{2} Computational Proteomics Unit, Cambridge Systems Biology
Centre, University of Cambridge, Tennis Court Road, Cambridge, CB2
1GA, UK.
\\
\bf{3} Applied Bioinformatics and Department of Computer Science,
University of Tübingen, D-72074 Tübingen, Germany.
\\
\bf{4} Medizinisches Proteom-Center, Ruhr-Universität Bochum,
Universitätsstr. 150, D-44801 Bochum, Germany.
\\
\bf{5} Department of Pathology, University of Michigan, Ann Arbor,
Michigan 48109, USA.
\\
\bf{6} Institute of Plant Biology and Biotechnology, University of
Muenster, Schlossplatz 8, 48143 Muenster, Germany.
\\
\bf{7} Centre for Mathematical Sciences, University of Cambridge,
Wilberforce Road, Cambridge CB3 0WA, UK.
\\
\bf{8} National Center for Supercomputing Applications \&
Graduate School of Library and Information Science, University of
Illinois, 1205 W. Clark St., Urbana, Illinois 61801, USA.
\\
\bf{9} MIT Laboratory for Computational Physiology, Institute for
Medical Engineering and Science, Massachusetts Institute of
Technology, Cambridge, MA 02142, USA.
\\
\bf{10} Centre for Interdisciplinary Research in Computational
Algebra, University of St Andrews, St Andrews, Fife, KY16 9SX, UK.
\\
\bf{11} Department of Molecular Biology and Biochemistry, Markey
Cancer Center, Resource Center for Stable Isotope-Resolved
Metabolomics, University of Kentucky, 800 Rose Street Lexington, KY
40536-0093, USA.

@@

The authors would like to thank C. Titus Brown, Chris Fields and an
anonymous reviewer for their helpful comments in improving the
manuscript. We would also like to thank C. Titus Brown from
advertising contributions to the manuscript on social media, leading
to further contributions and improvements. We also thank Peter Cock
(peterjc) and and Kai Blin (kblin) for helpful suggestion contributed
directly though GitHub.

>>>>

Yasset Perez-Riverol\textsuperscript{1,*}
Laurent Gatto\textsuperscript{2},
Rui Wang\textsuperscript{1}, 
Timo Sachsenberg \textsuperscript{3},
Julian Uszkoreit\textsuperscript{4},
Felipe da Veiga Leprevost\textsuperscript{5},
Christian Fufezan\textsuperscript{6},
Tobias Ternent\textsuperscript{1},
Stephen J. Eglen\textsuperscript{7}, 
Daniel S. Katz\textsuperscript{8}, 
Tom J. Pollard\textsuperscript{9}, 
Alexander Konovalov\textsuperscript{10},
Robert M Flight\textsuperscript{11},
Kai Blin\textsuperscript{12},
Juan Antonio Vizcaíno\textsuperscript{1,*}

@@

\bf{1} European Molecular Biology Laboratory, European Bioinformatics
Institute (EMBL-EBI), Wellcome Trust Genome Campus, Hinxton,
Cambridge, CB10 1SD, UK.
\\
\bf{2} Computational Proteomics Unit, Cambridge Systems Biology
Centre, University of Cambridge, Tennis Court Road, Cambridge, CB2
1GA, UK.
\\
\bf{3} Applied Bioinformatics and Department of Computer Science,
University of Tübingen, D-72074 Tübingen, Germany.
\\
\bf{4} Medizinisches Proteom-Center, Ruhr-Universität Bochum,
Universitätsstr. 150, D-44801 Bochum, Germany.
\\
\bf{5} Department of Pathology, University of Michigan, Ann Arbor,
Michigan 48109, USA.
\\
\bf{6} Institute of Plant Biology and Biotechnology, University of
Muenster, Schlossplatz 8, 48143 Muenster, Germany.
\\
\bf{7} Centre for Mathematical Sciences, University of Cambridge,
Wilberforce Road, Cambridge CB3 0WA, UK.
\\
\bf{8} National Center for Supercomputing Applications \& Graduate
School of Library and Information Science, University of Illinois,
1205 W. Clark St., Urbana, Illinois 61801, USA.
\\
\bf{9} MIT Laboratory for Computational Physiology, Institute for
Medical Engineering and Science, Massachusetts Institute of
Technology, Cambridge, MA 02142, USA.
\\
\bf{10} Centre for Interdisciplinary Research in Computational
Algebra, University of St Andrews, St Andrews, Fife, KY16 9SX, UK.
\\
\bf{11} Department of Molecular Biology and Biochemistry, Markey
Cancer Center, Resource Center for Stable Isotope-Resolved
Metabolomics, University of Kentucky, 800 Rose Street Lexington, KY
40536-0093, USA.
\\
\bf{12} The Novo Nordisk Foundation Center for Biosustainability,
Technical University of Denmark, Kogle Alle 6, 2970 Hørsholm, Denmark

@@

The authors would like to thank C. Titus Brown, Chris Fields and an
anonymous reviewer for their helpful comments in improving the
manuscript. We would also like to thank C. Titus Brown from
advertising contributions to the manuscript on social media, leading
to further contributions and improvements. We also thank Peter Cock
(peterjc) for helpful suggestion contributed directly though GitHub.
